### 2018-07-18 README.Rmd
synonymous changes

```{r install, eval = FALSE}
library("BiocInstaller")
biocLite("MSnbase")
```

If you need the github version (not recommended unless you know what
you are doing)

```{r installgh, eval = FALSE}
biocLite("lgatto/MSnbase")
```

>>>>

```{r install, eval = FALSE}
install.packages("BiocManager")

```

If you need the github version (not recommended unless you know what
you are doing), use

```{r installgh, eval = FALSE}
BiocManager::install("lgatto/MSnbase")
```
